Simulations

### 2017-10-21 3-simus.Rmd
okay?

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees(TTree, "ttrees", pheno.all, ind.train, ind.test, n.trees = 100)
  )
  print(res)
  saveRDS(res, file = res.file)
}
```

>>>>

  # Get results from all methods
  res <- bind_rows(
    PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees(TTree, "backingfiles/ttrees", pheno.all, ind.train, ind.test, n.trees = 100)
  )
  print(res)
  params[["res"]] <- list(res)
  saveRDS(unnest(param1, res), file = res.file)
}
```
